Contextual Identity: Towards Usable Privacy

### 2013-02-28 paper.tex
trivial tweaks, nothing substantial

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online environments~\cite{delete}. Managing contextual identities
online has become increasingly difficult and fraught with mistakes; we must
provide users with better tools to control their contextual identities.

@@

Barth, Datta, Mitchell, and Nissenbaum provide a formal model for contextual
integrity of user data~\cite{barth}. The contextual integrity model focuses on
the flow of personal information in terms of knowledge states held by agents
acting in given roles, and works well for modeling privacy legislation such as
HIPPA and COPPA. Two drawbacks of this work are that it does not
model information where the subject involves more than one person, and it
only takes the type of information into account rather than the content or tone
of the information.  ``Bob told Alice that Charlie cooked a
delicious dinner'' is out of scope of the model.  In the context of social
networks, information is rarely about a single person, and the tone of the
message is as important to user effect as the content of the message.

@@

\section{Contextual identity violations}
We consider it a contextual identity violation when
multiple contextual identities are linked without the user's permission, or the
user cannot control which contextual identity is presented to a given audience.

>>>>

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will often eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online environments~\cite{delete}. Managing contextual identities
online has become increasingly difficult and fraught with mistakes; we must
provide users with better tools to control their contextual identities.

@@

Barth, Datta, Mitchell, and Nissenbaum provide a formal model for contextual
integrity of user data~\cite{barth}. The contextual integrity model focuses on
the flow of personal information in terms of knowledge states held by agents
acting in given roles, and works well for modeling privacy legislation such as
HIPPA and COPPA. Two limitations of this work are that it does not
model information where the subject involves more than one person, and it
only takes the type of information into account rather than the content or tone
of the information.  ``Bob told Alice that Charlie cooked a
delicious dinner'' is out of scope of the model.  In the context of social
networks, information is rarely about a single person, and the tone of the
message is as important to user effect as the content of the message.

@@

\section{Contextual identity violations}
We consider it a contextual identity violation when
multiple contextually-separate identities are linked without the user's
permission, or when the user cannot select which contextual identity is
presented to a given audience.
